Baseline centering problem

### 2018-11-10 paper/advup_uniquesol.tex

>>>>

To train $b$ it is important to either use a very small learning rate, or
experience replay from past transitions, or have several independent
trajectories. Otherwise, a large learning rate
for $b$ just results in $b$ being equal to the average of the recent
Bellman gaps, thus erasing the training signal for $V$. One way to select
transitions to train $b$ is as follows. ($b$ does not have to follow the
same distribution for $s$, but it has to use the same policy for $a$
given $s$... so reusing
past transitions is
delicate if policy changes.)
